# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r}
localFile<-"repdata-data-activity.zip"
unzip(localFile)
localFile<-"activity.csv"
dataMov<-read.csv(localFile)

```

## What is mean total number of steps taken per day?

```{r mean}
summ<-aggregate(. ~ date, data=dataMov[,c(1:2)], FUN=sum,na.rm = TRUE)
barplot(summ$steps,names.arg=summ$date,
        main="Total number of steps taken each day",
        xlab="date",ylab="steps")
meanandMedianDay<-aggregate(. ~ date, data=dataMov[,c(1:2)], FUN=mean,na.rm = TRUE)

colnames(meanandMedianDay)[2]<-"Mean"
medianDay<-aggregate(. ~ date, data=dataMov, FUN=median, na.rm = TRUE)
meanandMedianDay$Median<-medianDay$steps
print(meanandMedianDay)
```


## What is the average daily activity pattern?
```{r timeseries}
dataMovts<-ts(dataMov)
plot(dataMovts,type="l",main="Time Series")
```

## Imputing missing values
Number of values with NA data:
```{r NAcount}
nrow(dataMov[is.na(dataMov$steps),])

```
Devising a strategy for filling in all of the missing values in the dataset:  mean of the interval across all data.
Filling...
```{r filling}
#New data set
meanInterval<-aggregate(. ~ interval, data=dataMov[,c(1,3)], FUN=mean,na.rm = TRUE)
colnames(meanInterval)[2]<-"MeanInterval"
dataMovNew<-merge(dataMov,meanInterval)
for(i in 1:nrow(dataMovNew))
   {
       if (is.na(dataMovNew$steps[i]))
          dataMovNew$steps[i]=dataMovNew$MeanInterval[i]
   }
#Now calculations with new data
summNew<-aggregate(. ~ date, data=dataMovNew[,c(3,2)], FUN=sum,na.rm = TRUE)
barplot(summNew$steps,names.arg=summNew$date,
        main="Total number of steps taken each day.(NA replaced)",
        xlab="date",ylab="steps")

meanandMedianDayNew<-aggregate(. ~ date, data=dataMovNew[,c(3,2)], FUN=mean,na.rm = TRUE)

colnames(meanandMedianDayNew)[2]<-"Mean"
medianDayNew<-aggregate(. ~ date, data=dataMovNew[,c(3,2)], FUN=median, na.rm = TRUE)
meanandMedianDayNew$Median<-medianDayNew$steps
print(meanandMedianDayNew)

```
Do these values differ from the estimates from the first part of the assignment? 
YES. But Only for days with NA values. 

What is the impact of imputing missing data on the estimates of the total daily number of steps?

Is a great impact because there are missing data for full days not only random values some days. For instance the first day of data hava all NA values for steps.



## Are there differences in activity patterns between weekdays and weekends?

```{r weekends}
#as.factor(strftime(as.Date(dataMovNew$date),format="%u"))

dataMovNew$day<-as.numeric(strftime(as.Date(dataMovNew$date),format="%u"))
dataMovNew$dayChar[dataMovNew$day<6]<-"WeekDay"
dataMovNew$dayChar[dataMovNew$day>5]<-"WeekEnd"
dataMovNew$weekDay<-as.factor(dataMovNew$dayChar)
dataMovNew$dayChar<-NULL



#Final plot with lattice
library(lattice)
interWeekday<-aggregate(steps ~ weekDay+interval, data=dataMovNew, FUN=mean,na.rm = TRUE)
xyplot(steps ~ interval | weekDay, data = interWeekday, layout = c(1, 2),
      type ="l",ylab="Number of Steps", xlab="Interval")


```
